A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-08-26 talk/talk.tex
Colour tweaks

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}

\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

@@

\setbeamerfont{block title}{size={}}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=white}
\setbeamercolor*{palette secondary}{use=structure,fg=black,bg=uofgcobalt}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One variable for each vertex in the pattern graph, with the domains being the vertices
            of the target graph.
        \item If two vertices are adjacent in the pattern, their values must be adjacent
            in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item All pattern vertices must be given different values.
        \item Often enhanced: for example, we can filter based upon degree.
        \item Another perspective: the variables describe an injective mapping from the pattern to
            the target, which preserves adjacency.
    \end{itemize}
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item VF2: backtracking search, interesting heuristics. Widely used. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. \emph{Luigi P.
                Cordella, Pasquale Foggia, Carlo Sansone and Mario Vento}. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

        \item LAD: locally all-different, and neighbourhood degree sequences. \\[0.1cm]
            {\scriptsize AllDifferent-based filtering for subgraph isomorphism. \emph{Christine
                Solnon}.  Artif. Intell., 2010.}
        \item SND: distance-based filtering. \\[0.1cm]
            {\scriptsize Scoring-Based Neighborhood Dominance for the Subgraph Isomorphism Problem.
                \emph{Gilles Audemard, Christophe Lecoutre, Mouny Samy Modeliar, Gilles
            Goncalves and Daniel Porumbel}. CP 2014.}
    \end{itemize}
\end{frame}

@@

        \item When LAD and SND fail, they often manage less than one recursive call per second,
            particularly with larger target graphs.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Our Approach}
    \begin{itemize}
        \item Cheaper inference: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive preprocessing once at the top of search, rather than computing distances and
            degree sequences during search.
        \item FC-CBJ instead of MAC:
            \begin{itemize}
                \item A counting-based all-different propagator, which does more
                    than pairwise-$\ne$ AC but less than GAC.
                \item CBJ without explicit conflict sets, and without modifying propagators.
            \end{itemize}
        \item Bit-parallelism for all major operations.
        \item Thread-parallel search:
            \begin{itemize}
                \item Safe, deterministic search via nested parallel folds.
                \item Explicit early work-stealing, to fake discrepancy search.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

    \only<3> {
        \begin{itemize}
            \item We can do something stronger: rather than looking at distances, we can look at
                (simple) paths, and we can count how many there are.

            \item This is \NP-hard in general, but only lengths 2 and 3 and counts of 2 and 3 are
                useful in practice.

            \item We construct these graph pairs once, at the top of search, and use them for
                degree-based filtering at the top of search, and ``adjacency'' filtering during
                search.
        \end{itemize}
    }
\end{frame}

\begin{frame}{Counting-Based All-Different}
    \begin{itemize}
        \item One pass through the variables, from smallest domain to largest.

        \item Track unions of domains as we go along.

        \item Eliminate any detected Hall sets from future variables.

        \item This can miss some deletions, but has a very fast bitset implementation for large
            domains.
    \end{itemize}
\end{frame}

>>>>

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}

\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgrust}{rgb}{0.603922, 0.227451, 0.023529}
\definecolor{uofgburgundy}{rgb}{0.490196, 0.133333, 0.223529}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

@@

\setbeamerfont{block title}{size={}}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=white}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=uofgheather}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One \textcolor{uofgrose}{variable for each vertex in the pattern} graph,
        with the \textcolor{uofgrose}{domains being the vertices of the target} graph.
    \item If two vertices are \textcolor{uofgrose}{adjacent in the pattern}, their
        \textcolor{uofgrose}{values must be adjacent} in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item Each pattern vertex must be given a \textcolor{uofgrose}{different value}.
        \item Often enhanced: for example, we can filter based upon degree.
        \item Another perspective: find an \textcolor{uofgrose}{injective mapping} from the
            pattern to the target, which \textcolor{uofgrose}{preserves adjacency}.
    \end{itemize}
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item \textcolor{uofgthistle}{VF2}: backtracking search, interesting heuristics. Widely used. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. \emph{Luigi P.
                Cordella, Pasquale Foggia, Carlo Sansone and Mario Vento}. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

        \item \textcolor{uofgthistle}{LAD}: locally all-different, and neighbourhood degree sequences. \\[0.1cm]
            {\scriptsize AllDifferent-based filtering for subgraph isomorphism. \emph{Christine
                Solnon}.  Artif. Intell., 2010.}

        \item \textcolor{uofgthistle}{SND}: distance-based filtering. \\[0.1cm]
            {\scriptsize Scoring-Based Neighborhood Dominance for the Subgraph Isomorphism Problem.
                \emph{Gilles Audemard, Christophe Lecoutre, Mouny Samy Modeliar, Gilles
            Goncalves and Daniel Porumbel}. CP 2014.}
    \end{itemize}
\end{frame}

@@

        \item When LAD and SND fail, they often manage less than \textcolor{uofgthistle}{one
            recursive call per second}, particularly with larger target graphs.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Our Approach}
    \begin{itemize}
        \item \textcolor{uofgthistle}{Cheaper inference}: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive \textcolor{uofgthistle}{preprocessing once} at the top of search, rather
            than computing distances and degree sequences during search.
        \item FC-CBJ instead of MAC:
            \begin{itemize}
                \item A \textcolor{uofgthistle}{counting-based all-different} propagator, which does more
                    than pairwise-$\ne$ AC but less than GAC.
                \item CBJ \textcolor{uofgthistle}{without explicit conflict sets}, and without modifying propagators.
            \end{itemize}
        \item \textcolor{uofgthistle}{Bit-parallelism} for all major operations.
        \item \textcolor{uofgthistle}{Thread-parallel} search:
            \begin{itemize}
                \item Safe, deterministic search via nested parallel folds.
                \item Explicit early work-stealing, to fake discrepancy search.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

    \only<3> {
        \begin{itemize}
            \item We can do something stronger: rather than looking at distances, we can look at
                \textcolor{uofgthistle}{(simple) paths}, and we can count how many there are.

            \item This is \NP-hard in general, but only \textcolor{uofgthistle}{lengths 2 and 3} and
                counts of 2 and 3 are useful in practice.

            \item We construct these graph pairs \textcolor{uofgthistle}{once, at the top of
                search}, and use them for degree-based filtering at the top of search, and
                ``adjacency'' filtering during search.
        \end{itemize}
    }
\end{frame}

\begin{frame}{Counting-Based All-Different}
    \begin{itemize}
        \item \textcolor{uofgthistle}{One pass} through the variables, from smallest domain to largest.

        \item Track \textcolor{uofgthistle}{unions of domains} as we go along.

        \item Eliminate \textcolor{uofgthistle}{any detected Hall sets} from future variables.

        \item This \textcolor{uofgthistle}{can miss some deletions}, but has a very fast bitset
            implementation for large domains.
    \end{itemize}
\end{frame}
